---
title: "Suspended Mines Extension"
author: "Reproduction Group 3"
date: '2022-05-10'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(sandwich)
library(haven)
library(estimatr)
library(tidyverse)

# load data
mininglocal <- read_dta("mininglocal.dta")
```

## Table 1
# The only difference between these regressions and the original table 1 is that we do not subset the data to exclude areas with suspended mines. 

# Table 1, regression 1
```{r}
t1r1_withsusp <- lm_robust(
  formula = bribe_police ~ active50 + inactive50 + urban + age + age2 + female + education + factor(country) + factor(year),
  se_type="stata", 
  cluster = cluster,
  data = mininglocal)
summary(t1r1_withsusp)
```

# Table 1, regression 2
```{r}
t1r2_withsusp <- lm_robust(
  formula = bribe_permit ~ active50 + inactive50 + urban + age + age2 + female + education + factor(country) + factor(year),
  se_type="stata", 
  cluster = cluster,
  data = mininglocal)
summary(t1r2_withsusp)
```

# table 1, regression 3
```{r}
t1r3_withsusp <- lm_robust(
  formula = local_corruption ~ active50 + inactive50 + urban + age + age2 + female + education + factor(country) + factor(year),
  se_type="stata", 
  cluster = cluster,
  data = mininglocal)
summary(t1r3_withsusp)
```

# table 1, regression 4
```{r}
t1r4_withsusp <- lm_robust(
  formula = corruption_police ~ active50 + inactive50 + urban + age + age2 + female + education + factor(country) + factor(year),
  se_type="stata", 
  cluster = cluster,
  data = mininglocal)
summary(t1r4_withsusp)
```

## Table 2
# The only difference between these regressions and the original table 2 is that we do not subset the data to exclude areas with suspended mines. 

# Table 2 regression 1
```{r}
t2r1_withsusp <- lm_robust(
  formula = bribe_police ~ active50 + factor(minefixed50) + urban + age + age2 + female + education + as.factor(year)-1,
  se_type="stata", 
  cluster = minefixed50,
  data = mininglocal)

summary(t2r1_withsusp)
```


# table 2 regression 2
```{r}
t2r2_withsusp <- lm_robust(
  formula = bribe_permit ~ active50 + factor(minefixed50) + urban + age + age2 + female + education + as.factor(year)-1,
  se_type="stata", 
  cluster = minefixed50,
  data = mininglocal)

summary(t2r2_withsusp)
```

# table 2 regression 3
```{r}
t2r3_withsusp <- lm_robust(
  formula = local_corruption ~ active50 + factor(minefixed50) + urban + age + age2 + female + education + as.factor(year)-1,
  se_type="stata", 
  cluster = minefixed50,
  data = mininglocal)

summary(t2r3_withsusp)
```

# table 2 regression 4
```{r}
t2r4_withsusp <- lm_robust(
  formula = corruption_police ~ active50 + factor(minefixed50) + urban + age + age2 + female + education + as.factor(year)-1,
  se_type="stata", 
  cluster = minefixed50,
  data = mininglocal)

summary(t2r4_withsusp)
```

## Table 3

# The only difference between these regressions and the original table 3 is that we do not subset the data to exclude areas with suspended mines. 

# Clustering observations
```{r}
# create opening_year = interview year - years since mine first opened 
# replace opening_year=NA if active50=0
df3 <- mininglocal %>%
  mutate(opening_year = int_year - yearssince_active50) %>%
  mutate(opening_year = replace(opening_year, active50==0, NA))

# cluster data by location and year: take the mean of respondent data for each location/year cluster, take the first datpoint for variables that are fixed in each cluster
df3.a <- df3 %>%
  group_by(cluster, int_year, year) %>%
  summarise(
    across(
      c(active50,
        inactive50,
        suspended50,
        opening_year,
        median,
        mean,
        countrycode),
      ~ first(.x)),
    across(
      c(age,
      police,
      bribe_police,
      urban,
      age,
      age2,
      female,
      education),
      ~ mean(.x, na.rm=TRUE)),
    across(
      starts_with("_"),
      ~ first(.x))
    )

```

# table 3 regression 1
```{r}
t3r1_withsusp <- lm_robust(median ~
                     active50 + inactive50
                   + urban
                   + age
                   + age2
                   + female
                   + education
                   + factor(countrycode) +  factor(int_year),
                   se_type="stata",
                   cluster = cluster, 
                   data = df3.a)
summary(t3r1_withsusp)
```

# table 3 regression 2
```{r}
t3r2_withsusp <- lm_robust(bribe_police ~
                     median
                   + urban
                   + age
                   + age2
                   + female
                   + education
                   + factor(countrycode) +  factor(int_year),
                   se_type="stata",
                   cluster = cluster, 
                   data = df3.a)
summary(t3r2_withsusp)

```

# Table 3 regression 3
```{r}
t3r3_withsusp <- lm_robust(bribe_police ~
                     active50 + inactive50
                   + median
                   + urban
                   + age
                   + age2
                   + female
                   + education
                   + factor(countrycode) +  factor(int_year),
                   se_type="stata",
                   cluster = cluster, 
                   data = df3.a)
summary(t3r3_withsusp)
```

# Table 3 regression 4
```{r}
t3r4_withsusp <- lm_robust(bribe_police ~
                     active50*median
                   + urban
                   + age
                   + age2
                   + female
                   + education
                   + factor(countrycode) +  factor(int_year),
                   se_type="stata",
                   cluster = cluster, 
                   data = df3.a)
summary(t3r4_withsusp)
```
